---
author: Enrique Mérida Casermeiro, Domingo López-Rodríguez, Juan Miguel Ortiz-de-Lazcano-Lobato
Status: Published
date: '2006-04-01'
slug: 2006-esann
title: Enhanced maxcut clustering with multivalued neural networks and functional
  annealing
categories:
- Combinatorial optimization
- Neural networks
header_image: ~
details: ESANN 2006 Proceedings - 14th European Symposium on Artificial Neural Networks,
  <em>pp. 25&ndash;30</em>
doi: ''
link: 2006-esann/paper.pdf
project: ''
keywords: Combinatorial optimization, Optimization, Combinatorial optimization problems,
  Its efficiencies, Local optima, MAX-CUT problem, Multi-valued, NP Complete, Optimization
  method, Recurrent models, Recurrent neural networks
---

# Abstract

In this work a new algorithm to improve the performance of optimization methods, by means of avoiding certain local optima, is described. Its theoretical bases are presented in a rigorous, but intuitive, way. It has been applied concretely to the case of recurrent neural networks, in particular to MREM, a multivalued recurrent model, that has proved to obtain very good results when dealing with NP-complete combinatorial optimization problems. In order to show its efficiency, the well-known MaxCut problem for graphs has been selected as benchmark. Our proposal outperforms other specialized and powerful techniques, as shown by simulations.

```{r citing}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  cat("# Cites\n")
  cat("The following graph plots the number of cites received by this work from its publication, on a yearly basis.\n")
  
}
```

```{r citing2}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  source(here::here("scripts", "manage_publications.R"))
  df <- readRDS("citation_history.rds")
  plot_citation_history(df)
  
}
```


# Citation

Please, cite this work as:

```{r citation1}
#| results: asis
#| echo: false
#| shortcodes: true
this_folder <- here::here(
  'publications', 
  'conferences', 
  rmarkdown::metadata$slug
  )
library(RefManageR)
s <- ReadBib(file.path(this_folder, 'cite.bib'))
NoCite(s) 
options(width = 1000) 
txt <- capture.output(PrintBibliography(s, .opts = list(bib.style = 'alphabetic', style = 'markdown')))
cat(txt)
```

  

::: {.callout-note appearance="minimal" collapse=true}

## BibTeX

```{r citation2}
#| warning: false
#| results: asis
#| echo: false

source(here::here(
  "scripts", 
  'format_bibtex.R'))

cat(
  format_bibtex(
    file.path(
      this_folder, 
      'cite.bib')))
```

:::
