---
author: Domingo López-Rodríguez, E. Mérida-Casermeiro, G. Galán-Marín, J.M. Ortiz-de-Lazcano-Lobato
Status: Published
date: '2007-01-01'
slug: 2007-ki
title: 'Stochastic functional annealing as optimization technique: Application to
  the traveling salesman problem with recurrent networks'
categories:
- Neural networks
- Combinatorial optimization
header_image: ~
details: Lecture Notes in Computer Science (including subseries Lecture Notes in Artificial
  Intelligence and Lecture Notes in Bioinformatics), (4667 LNAI), <em>pp. 397-411</em>
doi: 10.1007/978-3-540-74565-5_30
link: 2007-ki/paper.pdf
project: ''
keywords: Computational efficiency, Convergence of numerical methods, Finite difference
  method, Hopfield neural networks, Traveling salesman problem, Discrete neural networks,
  Stochastic functional annealing, Stochastic methods, Stochastic models
---

# Abstract

In this work, a new stochastic method for optimization problems is developed. Its theoretical bases guaranteeing the convergence of the method to a minimum of the objective function are presented, by using quite general hypotheses. Its application to recurrent discrete neural networks is also developed, focusing in the multivalued MREM model, a generalization of Hopfield's. In order to test the efficiency of this new method, we study the well-known Traveling Salesman Problem. Experimental results will show that this new model outperforms other techniques, achieving better results, even on average, than other methods. © Springer-Verlag Berlin Heidelberg 2007.

```{r citing}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  cat("# Cites\n")
  cat("The following graph plots the number of cites received by this work from its publication, on a yearly basis.\n")
  
}
```

```{r citing2}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  source(here::here("scripts", "manage_publications.R"))
  df <- readRDS("citation_history.rds")
  plot_citation_history(df)
  
}
```


# Citation

Please, cite this work as:

```{r citation1}
#| results: asis
#| echo: false
#| shortcodes: true
this_folder <- here::here(
  'publications', 
  'conferences', 
  rmarkdown::metadata$slug
  )
library(RefManageR)
s <- ReadBib(file.path(this_folder, 'cite.bib'))
NoCite(s) 
options(width = 1000) 
txt <- capture.output(PrintBibliography(s, .opts = list(bib.style = 'alphabetic', style = 'markdown')))
cat(txt)
```

  

::: {.callout-note appearance="minimal" collapse=true}

## BibTeX

```{r citation2}
#| warning: false
#| results: asis
#| echo: false

source(here::here(
  "scripts", 
  'format_bibtex.R'))

cat(
  format_bibtex(
    file.path(
      this_folder, 
      'cite.bib')))
```

:::
