---
author: Ángel Mora Bonilla, Domingo López-Rodríguez, Enrique Mérida-Casermeiro
Status: Published
date: '2007-08-01T00:00:00Z'
slug: 2007-blended
title: 'HECACEJ: B-Learning Tool for Static Content Creation in Joomla!'
categories: E-learning
header_image: ~
details: <em>Workshop on Blended Learning</em> 2007
doi: ''
link: 2007-blended/paper.pdf
project: ~
keywords: B-learning, LMS, CMS, Joomla!, Integration of tools
---

# Abstract

In this work we have reviewed the concepts of Learning Managementystem (LMS), Learning Content Management System (LCMS) and Content Management System (CMS). Their main features are studied, and a comparison among them is presented, along with a summary of some well- known integrations between LMS and CMS. Another important point in this work is presenting HECACEJ, a B-learning tool designed to create static content in Joomla! This tool is a specific content manager for publishing the material for a subject, which does not need help from the administration menu of Joomla! (difficult to use by a non-expert professor) and is able to publish these contents in Joomla! main menu. This tool eases the publication of B- learning contents (class notes, past exams, professors' data, etc.) in a static web page that can be accessed from the main menu of the platform Joomla!, which provides facilities for manipulating the contents but it was not developed ad- hoc for our proposal.

```{r citing}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  cat("# Cites\n")
  cat("The following graph plots the number of cites received by this work from its publication, on a yearly basis.\n")
  
}
```

```{r citing2}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  source(here::here("scripts", "manage_publications.R"))
  df <- readRDS("citation_history.rds")
  plot_citation_history(df)
  
}
```


# Citation

Please, cite this work as:

```{r citation1}
#| results: asis
#| echo: false
#| shortcodes: true
this_folder <- here::here(
  'publications', 
  'conferences', 
  rmarkdown::metadata$slug
  )
library(RefManageR)
s <- ReadBib(file.path(this_folder, 'cite.bib'))
NoCite(s) 
options(width = 1000) 
txt <- capture.output(PrintBibliography(s, .opts = list(bib.style = 'alphabetic', style = 'markdown')))
cat(txt)
```

  

::: {.callout-note appearance="minimal" collapse=true}

## BibTeX

```{r citation2}
#| warning: false
#| results: asis
#| echo: false

source(here::here(
  "scripts", 
  'format_bibtex.R'))

cat(
  format_bibtex(
    file.path(
      this_folder, 
      'cite.bib')))
```

:::
