---
author:
- Ondrej Krídlo
- Domingo López-Rodríguez
- Lubomir Antoni
- Peter Eliaš
- Stanislav Krajči
- Manuel Ojeda-Aciego
Status: Published
selected: yes
date: '2023-08-03T00:00:00Z'
slug: 2023-insci
title: Connecting concept lattices with bonds induced by external information
categories: Formal concept analysis
header_image: ~
details: <em>Information Sciences</em>, vol. 648, november 2023, article 119498
doi: 10.1016/j.ins.2023.119498
link: 2023-insci/paper.pdf
project: 2023-valid
keywords: Formal Concept Analysis, Intercontextual structures, Bonds
---


# Abstract

In Formal Concept Analysis (FCA), $\mathcal L$-bonds represent relationships between $\mathcal L$-formal contexts. Choosing the appropriate bond between $\mathcal L$-fuzzy formal contexts is an important challenge for its application in recommendation tasks. Recent work introduced two constructions of bonds, given by direct products of two $\mathcal L$-fuzzy formal contexts, and showed their usefulness in a particular application. In this paper, we present further theoretical and experimental results on these constructions; in particular, we provide extended interpretations of both rigorous and benevolent concept-forming operators, introduce new theoretical properties of the proposed bonds to connect two concept lattices given external information, and finally present the experimental study of the upper bounds.

```{r citing}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  cat("# Cites\n")
  cat("The following graph plots the number of cites received by this work from its publication, on a yearly basis.\n")
  
}
```

```{r citing2}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  source(here::here("scripts", "manage_publications.R"))
  df <- readRDS("citation_history.rds")
  plot_citation_history(df)
  
}
```


# Citation

Please, cite this work as:

```{r citation1}
#| results: asis
#| echo: false
#| shortcodes: true
this_folder <- here::here(
  'publications', 
  'journals', 
  rmarkdown::metadata$slug
  )
library(RefManageR)
s <- ReadBib(file.path(this_folder, 'cite.bib'))
NoCite(s) 
options(width = 1000) 
txt <- capture.output(PrintBibliography(s, .opts = list(bib.style = 'alphabetic', style = 'markdown')))
cat(txt)
```

  

::: {.callout-note appearance="minimal" collapse=true}

## BibTeX

```{r citation2}
#| warning: false
#| results: asis
#| echo: false

source(here::here(
  "scripts", 
  'format_bibtex.R'))

cat(
  format_bibtex(
    file.path(
      this_folder, 
      'cite.bib')))
```

:::
