---
author: Enrique Mérida Casermeiro, Domingo López-Rodríguez, Juan Miguel Ortiz-de-Lazcano-Lobato
Status: Published
date: '2007-01-01'
slug: 2007-ifip
title: Image Compression with Competitive Networks and Pre-fixed Prototypes
categories:
- Image processing
- Competitive learning
- Neural networks
header_image: ~
details: IFIP International Federation for Information Processing, (247), <em>pp.
  339&ndash;346</em>
doi: 10.1007/978-0-387-74161-1\_37
link: 2007-ifip/paper.pdf
project: ''
keywords: Image compression, Image quality, Classical methods, Competitive network,
  Competitive neural network, Compressed images, Computational time, Image compression
  techniques, Peak signal to noise ratio, Artificial intelligence
---

# Abstract

Image compression techniques have required much attention from the neural networks community for the last years. In this work we intend to develop a new algorithm to perform image compression based on adding some pre-fixed prototypes to those obtained by a competitive neural network. Prototypes are selected to get a better representation of the compressed image, improving the computational time needed to encode the image and decreasing the code-book storage necessities of the standard approach. This new method has been tested with some well-known images and results proved that our proposal outperforms classical methods in terms of maximizing peak-signal-to-noise-ratio values. © 2007 International Federation for Information Processing.

```{r citing}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  cat("# Cites\n")
  cat("The following graph plots the number of cites received by this work from its publication, on a yearly basis.\n")
  
}
```

```{r citing2}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  source(here::here("scripts", "manage_publications.R"))
  df <- readRDS("citation_history.rds")
  plot_citation_history(df)
  
}
```


# Citation

Please, cite this work as:

```{r citation1}
#| results: asis
#| echo: false
#| shortcodes: true
this_folder <- here::here(
  'publications', 
  'conferences', 
  rmarkdown::metadata$slug
  )
library(RefManageR)
s <- ReadBib(file.path(this_folder, 'cite.bib'))
NoCite(s) 
options(width = 1000) 
txt <- capture.output(PrintBibliography(s, .opts = list(bib.style = 'alphabetic', style = 'markdown')))
cat(txt)
```

  

::: {.callout-note appearance="minimal" collapse=true}

## BibTeX

```{r citation2}
#| warning: false
#| results: asis
#| echo: false

source(here::here(
  "scripts", 
  'format_bibtex.R'))

cat(
  format_bibtex(
    file.path(
      this_folder, 
      'cite.bib')))
```

:::
