---
author: E. López-Rubio, J.M. Ortiz-De-Lazcano-Lobato, Domingo López-Rodríguez, E.
  Mérida-Casermeiro, M. Del Carmen Vargas-González
Status: Published
date: '2006-09-01'
slug: 2006-icann2
title: Local selection of model parameters in probability density function estimation
categories: Neural networks
header_image: ~
details: Artificial Neural Networks - (ICANN) 2006, 16th International Conference,
  Lecture Notes in Computer Science (including subseries Lecture Notes in Artificial
  Intelligence and Lecture Notes in Bioinformatics), (4132 LNCS - II), <em>pp. 292-301</em>
doi: 10.1007/11840930_30
link: 2006-icann2/paper.pdf
project: ''
keywords: Gaussian noise (electronic), Mathematical models, Parameter estimation,
  Signal noise measurement, Automated estimation, Local intrinsic dimensionality,
  Local noise variance, Parzen window approach, Probability density function
---

# Abstract

Here we present a novel probability density estimation model. The classical Parzen window approach builds a spherical Gaussian density around every input sample. Our proposal selects a Gaussian specifically tuned for each sample, with an automated estimation of the local intrinsic dimensionality of the embedded manifold and the local noise variance. This leads to outperform other proposals where local parameter selection is not allowed, like the manifold Parzen windows. © Springer-Verlag Berlin Heidelberg 2006.

```{r citing}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  cat("# Cites\n")
  cat("The following graph plots the number of cites received by this work from its publication, on a yearly basis.\n")
  
}
```

```{r citing2}
#| echo: false
#| results: asis
#| warning: false
#| message: false

if (file.exists("citation_history.rds")) {
  
  source(here::here("scripts", "manage_publications.R"))
  df <- readRDS("citation_history.rds")
  plot_citation_history(df)
  
}
```


# Citation

Please, cite this work as:

```{r citation1}
#| results: asis
#| echo: false
#| shortcodes: true
this_folder <- here::here(
  'publications', 
  'conferences', 
  rmarkdown::metadata$slug
  )
library(RefManageR)
s <- ReadBib(file.path(this_folder, 'cite.bib'))
NoCite(s) 
options(width = 1000) 
txt <- capture.output(PrintBibliography(s, .opts = list(bib.style = 'alphabetic', style = 'markdown')))
cat(txt)
```

  

::: {.callout-note appearance="minimal" collapse=true}

## BibTeX

```{r citation2}
#| warning: false
#| results: asis
#| echo: false

source(here::here(
  "scripts", 
  'format_bibtex.R'))

cat(
  format_bibtex(
    file.path(
      this_folder, 
      'cite.bib')))
```

:::
